---
title: "Read Data"
output: html_notebook
---

# Task 01

Create a function that takes as input the path to a single .csv file in the specdata folder and creates
a data table from its contents. The data types in the output table have to match the data
(date is understood as a date).

# Solution of task 01

to write this function I will use *read.table*function


```{r function to read.table, echo=FALSE}
path_to <- "specdata/001.csv"

data_read_i <- function(path_to){
  data_tab <- read.table(file=path_to , header = T, sep = ',',colClasses =
                           c('Date','numeric','numeric','factor'))
  return(data_tab)
}

data_i <- data_read_i(path_to)

head(data_i)
```

# Task 02

Write a for loop that loops through all the file paths in the specdata folder and uses the function
written in previous point to read the data from the .csv files. Create a table with columns that show:

1. ID nr
2. the nr of rows in each of the read in tables 
3. The number of rows where atleast sulfate or nitrate data is not missing.

# Solution Task 02

```{r echo=FALSE}
k <- 0

file_names <- list.files('specdata', full.names = T)
for (file_i in file_names) {
  data_i <- data_read_i(file_i)
  ID <- data_i$ID[1]
  No_data_rows <- nrow(data_i)
  No_rows_not_NA_sulf <- !is.na(data_i$sulfate)
  No_rows_not_NA_nitr <- !is.na(data_i$nitrate)
  No_rows_not_NA <- No_rows_not_NA_sulf | No_rows_not_NA_nitr
  
  data_not_NA <- data_i[No_data_rows,]
  No_rows_not_NA <- nrow(data_not_NA)
  
  out_tab_i <- data.frame(ID,No_data_rows,No_rows_not_NA)
  
  if(k == 0){
    out_tab <- out_tab_i
    k <- 1
  }else{
    out_tab <- rbind(out_tab,out_tab_i)
  }
}

head(out_tab)
```

