---
title: "My Course Project"
output: html
---

In this investigation, we want to examine the model Sea level data (hydrodynamic models – HDM) compared with tide gauge data that is referenced to the geoid. and find biases between time series of medel and this tide gauges to improve the 

We have Dynamic Topography (DT) data of the Baltic sea in two ways:

1. Time history data of marine hydrodynamic model (NEMO-NORDIC)
2. Time history of DT observation in 16 station around the Estonia (Tide Gauge data)

We want to compare two time-history and validate the model data by the observations.

# Read Data
So, we read the files of data at the first. the Data is available for a year (2015)

```{r}
path_to <- "MyData/001.csv"

ReadData <- function(path_to){
  Table <- read.table(file = path_to , header = T, sep = ',', skip = 3)
  # In some data sheets, the names of col are different! so:
  names(Table) <- c('date', 'time','TG','Model_m','Model_cm')
  
  # Remove NaNs
  Table = Table[ , !apply( Table , 2 , function(x) all(is.na(x)) ) ]
  Table = na.omit(Table)
  
  Temp <- read.table(file = path_to , header = F, sep = ',', skip = 2 , nrows = 1)
  Table$Lon <- Temp$V2
  Table$Lat <- Temp$V3
  
  # creat a column as a Date with date format
  Table$Date <- as.POSIXct(paste(Table$date,Table$time),format = '%m/%d/%Y %H:%M:%OS',tz = 'UTC')

  return(Table)
}


Data <- ReadData(path_to)

head(Data)
```

Plot a station of tide gauge and show the difference between model and currect tide guage

```{r}
plot(Data$Date  , Data$TG , type = "l" , col = "blue")
lines(Data$Date  , Data$Model_cm , col = "red")
```

